Transformation of forecasts for evaluating predictive performance in an epidemiological context

### 2023-01-24 main.tex
Updates from Overleaf

As argued in Section \ref{sec:methods:vst}, the mean-variance, or mean-CRPS, relationship determines which transformation can serve as a VST. We can analyse this relationship empirically by running a regression that explains the CRPS as a function of the central estimate of the predictive distribution. We ran the regression
\begin{equation*}
    \log[\text{CRPS}(F, y)] = \alpha + \beta \times \log[\text{median}(F)], 
\end{equation*}
where the predictive distribution $F$ and the observation $y$ are on the natural scale. This is equivalent to
\begin{equation*}
    \text{CRPS}(F, y) = \exp(\alpha) \times \text{median}(F)^\beta, 
\end{equation*}
meaning that we estimate a polynomial relationship between the predictive median and achieved CRPS. Note that we are using predictive medians rather than means as only the former are available in the European COVID-19 Forecast Hub. As the CRPS of an ideal forecaster scales with the standard deviation (see Section \ref{sec:methods:vst}), a value of $\beta = 1$ would imply a quadratic median-variance relationship; the natural logarithm could then serve as a VST. A value of $\beta 0.5$ would imply a linear median-variance relationship, suggesting the square root as a VST. We applied the regression to case and death forecasts, pooled across horizons and stratified for one through four-week-ahead forecasts. Results are provided in Table \ref{tab:HUB-regression}. It can be seen that the estimates of $\beta$ always take a value somewhat below 1, implying a slightly sub-quadratic mean-variance relationship. The logarithmic transformation should thus approximately stabilize the variance (and CRPS), possibly leading to somewhat higher scores for smaller forecast targets. The square-root transformation, on the other hand, can be expected to still lead to higher CRPS values for targets of higher orders of magnitude.

@@

\begin{table}
\centering
\begin{tabular}{ccrrrrrr}
\toprule
Horizon & Target & $\alpha$ & $\beta$ & $\alpha_\sqrt{\ }$ & $\beta_\sqrt{\ }$ & $\alpha_\log$ & $\beta_\log$ \\
\midrule
all & all & -1.093 & 0.963 & -0.352 & 0.201 & 0.391 & 0.001\\
\addlinespace
all & Cases & 0.036 & 0.858 & 0.043 & 0.201 & 0.751 & -0.033\\
all & Deaths & -0.884 & 0.868 & 0.273 & 0.121 & 0.436 & -0.023\\
\addlinespace
1 & all & -1.402 & 0.923 & 0.320 & 0.088 & 0.318 & -0.014\\
2 & all & -1.221 & 0.967 & 0.112 & 0.164 & 0.364 & -0.003\\
3 & all & -1.001 & 0.984 & -0.094 & 0.241 & 0.410 & 0.008\\
4 & all & -0.757 & 0.986 & 0.000 & 0.299 & 0.469 & 0.015\\
\addlinespace
1 & Cases & -0.862 & 0.876 & 0.790 & 0.087 & 0.433 & -0.024\\
2 & Cases & -0.243 & 0.877 & 0.959 & 0.162 & 0.660 & -0.031\\
3 & Cases & 0.372 & 0.855 & 1.109 & 0.238 & 0.882 & -0.037\\
4 & Cases & 0.816 & 0.837 & 1.645 & 0.296 & 1.009 & -0.036\\
\addlinespace
1 & Deaths & -1.146 & 0.832 & 0.457 & 0.048 & 0.376 & -0.035\\
2 & Deaths & -0.981 & 0.867 & 0.443 & 0.084 & 0.416 & -0.028\\
3 & Deaths & -0.807 & 0.885 & 0.349 & 0.131 & 0.453 & -0.019\\
4 & Deaths & -0.602 & 0.891 & 0.125 & 0.194 & 0.501 & -0.011\\
\bottomrule
\end{tabular}
\caption{Coefficients of three regressions for the effect of the magnitude of the median forecast on expected scores. The first regression was 
$\log[\text{CRPS}(F, y)] = \alpha + \beta \times \log[\text{median}(F)], $ where $F$ is the predictive distribution and $y$ the observed value. The second one was 
$\text{CRPS}(F_{\log}, \log y) = \alpha_{\log} + \beta_{\log} \cdot \log{(\text{median}(F))},$ where $F_{\log}$ is the predictive distribution for $\log y$. The third one was $\text{CRPS}(F_{\sqrt{\ }}, \sqrt{y}) = \alpha_{sqrt{\ }} + \beta_{sqrt{\ }} \cdot \sqrt{(\text{median}(F))},$ where $F_{\sqrt{\ }}$ is the predictive distribution for $\sqrt{y}$.
}
\label{tab:HUB-regression}
\end{table}

To check the relationship after the transformation, we ran the regressions
\begin{equation*}
    \text{CRPS}(F_{\log}, \log y) = \alpha_{\log} + \beta_{\log} \cdot \log{(\text{median}(F))},
\end{equation*}
where $F_{\log}$ is the predictive distribution for $\log(y)$, and
\begin{equation*}
    \text{CRPS}(F_{\sqrt{\ }}, \sqrt{y}) = \alpha_{\sqrt{\ }} + \beta_{\sqrt{\ }} \cdot \sqrt{\text{median}(F)},
\end{equation*} 
where $F_{\sqrt{\ }}$ is the predictive distribution on the square-root scale. A value of $\beta_{\log} = 0$ (or $\beta_{\sqrt{\ } = 0}$, respectively, would imply that scores are independent of the median prediction after the transformation. A value smaller (larger) than 0 would imply that smaller (larger) targets lead to higher scores. As can be seen from Table \ref{tab:HUB-regression}, the results indeed indicate that small targets lead to larger average CRPS when using the log transform ($\beta_{\log} < 0$), while the opposite is true for the square-root transform ($\beta_{\sqrt{\ }} > 0$). The results of the three regressions are also displayed in Figure \ref{fig:HUB-regression}. In this empirical example, the log transformation thus helps (albeit not perfectly), to stabilise WIS values, and it does so more successfully than the square-root transformation. As can be seen from Figure \ref{fig:HUB-regression}, the expected CRPS scores for case targets with medians of 10 and 100,000 differ by more then a factor of ten for the square root transformation, but only a factor of around 2 for the logarithm.

>>>>

As argued in Section \ref{sec:methods:vst}, the mean-variance, or mean-CRPS, relationship determines which transformation can serve as a VST. We can analyse this relationship empirically by running a regression that explains the WIS (which approximates the CRPS) as a function of the central estimate of the predictive distribution. We ran the regression
\begin{equation*}
    \log[\text{WIS}(F, y)] = \alpha + \beta \times \log[\text{median}(F)], 
\end{equation*}
where the predictive distribution $F$ and the observation $y$ are on the natural scale. This is equivalent to
\begin{equation*}
    \text{WIS}(F, y) = \exp(\alpha) \times \text{median}(F)^\beta, 
\end{equation*}
meaning that we estimate a polynomial relationship between the predictive median and achieved WIS. Note that we are using predictive medians rather than means as only the former are available in the European COVID-19 Forecast Hub. As the WIS/CRPS of an ideal forecaster scales with the standard deviation (see Section \ref{sec:methods:vst}), a value of $\beta = 1$ would imply a quadratic median-variance relationship; the natural logarithm could then serve as a VST. A value of $\beta = 0.5$ would imply a linear median-variance relationship, suggesting the square root as a VST. We applied the regression to case and death forecasts, pooled across horizons and stratified for one through four-week-ahead forecasts. Results are provided in Table \ref{tab:HUB-regression}. It can be seen that the estimates of $\beta$ always take a value somewhat below 1, implying a slightly sub-quadratic mean-variance relationship. The logarithmic transformation should thus approximately stabilize the variance (and WIS), possibly leading to somewhat higher scores for smaller forecast targets. The square-root transformation, on the other hand, can be expected to still lead to higher WIS values for targets of higher orders of magnitude.

@@

\begin{table}
\centering
\begin{tabular}{ccrrrrrr}
\toprule
Horizon & Target & $\alpha$ & $\beta$ & $\alpha_\sqrt{\ }$ & $\beta_\sqrt{\ }$ & $\alpha_\log$ & $\beta_\log$ \\
\midrule
all & all & -1.093 & 0.963 & -0.352 & 0.201 & 0.391 & 0.001\\
\addlinespace
all & Cases & 0.036 & 0.858 & 0.043 & 0.201 & 0.751 & -0.033\\
all & Deaths & -0.884 & 0.868 & 0.273 & 0.121 & 0.436 & -0.023\\
\addlinespace
1 & all & -1.402 & 0.923 & 0.320 & 0.088 & 0.318 & -0.014\\
2 & all & -1.221 & 0.967 & 0.112 & 0.164 & 0.364 & -0.003\\
3 & all & -1.001 & 0.984 & -0.094 & 0.241 & 0.410 & 0.008\\
4 & all & -0.757 & 0.986 & 0.000 & 0.299 & 0.469 & 0.015\\
\addlinespace
1 & Cases & -0.862 & 0.876 & 0.790 & 0.087 & 0.433 & -0.024\\
2 & Cases & -0.243 & 0.877 & 0.959 & 0.162 & 0.660 & -0.031\\
3 & Cases & 0.372 & 0.855 & 1.109 & 0.238 & 0.882 & -0.037\\
4 & Cases & 0.816 & 0.837 & 1.645 & 0.296 & 1.009 & -0.036\\
\addlinespace
1 & Deaths & -1.146 & 0.832 & 0.457 & 0.048 & 0.376 & -0.035\\
2 & Deaths & -0.981 & 0.867 & 0.443 & 0.084 & 0.416 & -0.028\\
3 & Deaths & -0.807 & 0.885 & 0.349 & 0.131 & 0.453 & -0.019\\
4 & Deaths & -0.602 & 0.891 & 0.125 & 0.194 & 0.501 & -0.011\\
\bottomrule
\end{tabular}
\caption{Coefficients of three regressions for the effect of the magnitude of the median forecast on expected scores. The first regression was 
$\log[\text{WIS}(F, y)] = \alpha + \beta \times \log[\text{median}(F)], $ where $F$ is the predictive distribution and $y$ the observed value. The second one was 
$\text{WIS}(F_{\log}, \log y) = \alpha_{\log} + \beta_{\log} \cdot \log{(\text{median}(F))},$ where $F_{\log}$ is the predictive distribution for $\log y$. The third one was $\text{WIS}(F_{\sqrt{\ }}, \sqrt{y}) = \alpha_{sqrt{\ }} + \beta_{sqrt{\ }} \cdot \sqrt{(\text{median}(F))},$ where $F_{\sqrt{\ }}$ is the predictive distribution for $\sqrt{y}$.
}
\label{tab:HUB-regression}
\end{table}

To check the relationship after the transformation, we ran the regressions
\begin{equation*}
    \text{WIS}(F_{\log}, \log y) = \alpha_{\log} + \beta_{\log} \cdot \log{(\text{median}(F))},
\end{equation*}
where $F_{\log}$ is the predictive distribution for $\log(y)$, and
\begin{equation*}
    \text{WIS}(F_{\sqrt{\ }}, \sqrt{y}) = \alpha_{\sqrt{\ }} + \beta_{\sqrt{\ }} \cdot \sqrt{\text{median}(F)},
\end{equation*} 
where $F_{\sqrt{\ }}$ is the predictive distribution on the square-root scale. A value of $\beta_{\log} = 0$ (or $\beta_{\sqrt{\ }} = 0$, respectively, would imply that scores are independent of the median prediction after the transformation. A value smaller (larger) than 0 would imply that smaller (larger) targets lead to higher scores. As can be seen from Table \ref{tab:HUB-regression}, the results indeed indicate that small targets lead to larger average WIS when using the log transform ($\beta_{\log} < 0$), while the opposite is true for the square-root transform ($\beta_{\sqrt{\ }} > 0$). The results of the three regressions are also displayed in Figure \ref{fig:HUB-regression}. In this empirical example, the log transformation thus helps (albeit not perfectly), to stabilise WIS values, and it does so more successfully than the square-root transformation. As can be seen from Figure \ref{fig:HUB-regression}, the expected WIS scores for case targets with medians of 10 and 100,000 differ by more then a factor of ten for the square root transformation, but only a factor of around 2 for the logarithm.
